%
% Copyright (c) 2008-2014, TechnoPark Corp., Florida, USA
% All rights reserved. THIS IS PRIVATE DOCUMENTATION.
%
% Redistribution and use in source and binary forms, with or without modification, are PROHIBITED
% without prior written permission from the author. This product may NOT be used anywhere
% and on any computer except the server platform of TechnoPark Corp. located at
% www.technoparkcorp.com. If you received this code occacionally and without intent to use
% it, please report this incident to the author by email: privacy@technoparkcorp.com or
% by mail: 568 Ninth Street South 202 Naples, Florida 34102, the United States of America,
% tel. +1 (239) 243 0206, fax +1 (239) 236-0738.
%
\documentclass[10pt,letterpaper,oneside,twocolumn]{article}
\usepackage{fancyhdr,lastpage,titlesec,xtab}
\usepackage[hyperfootnotes=true]{hyperref}
\linespread{1.2}
\usepackage{array}

% comment out the next line and the document will
% lose the watermark
\chead{\begin{textblock}{15}(0,0)\tikz{\node [rotate=45, scale=18, text=black!10, font=\ttfamily\bfseries] at (0,0) {sample};}\end{textblock}\colorbox{black!10}{\color{red}{this is a not a real agreement, don't sign it}}}

\newcommand{\tpcInitials}       {Y.B.}
\newcommand{\engineerPrice}     {19.99}
\newcommand{\engineerName}      {Jeff Lebowski}
\newcommand{\engineerEmail}     {jeff.lebowski@tpc2.com}
\newcommand{\engineerPhone}     {+1 212 555 6677}
\newcommand{\engineerAddress}   {1st Street, 1}
\newcommand{\engineerCountry}   {USA}

\newcounter{parnum}
\setcounter{parnum}{1}
\newcommand{\N}[1]{\arabic{parnum}\refstepcounter{parnum}\label{#1}.}
\newcommand{\M}[1]{\vspace*{0pt}{\color{blue!50!black}\raggedright #1}}

\usepackage{array,setspace}
\usepackage{tikz}
    \usetikzlibrary{arrows}

\usepackage[absolute]{textpos}
    \TPGrid{16}{16}
\usepackage[top=2\TPVertModule, bottom=2\TPVertModule, left=2\TPHorizModule, right=2\TPHorizModule]{geometry}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\tpcTitle}{TechnoPark Corp. proprietary documentation}
\newcommand{\tpcAuthors}{TechnoPark Corp.}
\newcommand{\tpcFileName}{TPC-.pdf}
\hypersetup{bookmarks=false, unicode=false, pdftoolbar=true, pdfmenubar=true, pdffitwindow=false, pdftitle={\tpcTitle}, pdfauthor={TechnoPark Corp., \tpcAuthors}, pdfsubject={\tpcTitle}, pdfnewwindow=true, colorlinks=true, linkcolor=black, citecolor=black, filecolor=black, urlcolor=black}
\lfoot{
    \begin{textblock}{12}[0,1](2,15)
        \fontfamily{phv}\selectfont\scriptsize%
        {
        \begin{tabular*}{12\TPHorizModule}{@{\extracolsep{\fill}} lcr}
        {\color{blue}\normalfont\large\bfseries\tpcInitials} & & \\
        \rule{2\TPHorizModule}{0.5pt} & Page \#\thepage{} of \pageref{LastPage} & \rule{2\TPHorizModule}{0.5pt} \\
        TPC, initials & (c) Copyright TechnoPark Corp. & Engineer, initials \\
        \end{tabular*}}
    \end{textblock}
}

\renewcommand{\M}[1]{}

\renewcommand\thesection{\Roman{section}}
\titleformat{\section}
    {\fontsize{10pt}{11pt}\bfseries\fontfamily{phv}\selectfont\raggedright}
    {\thesection{}.}{1em}{}
\titlespacing{\section}
    {0em}{0em}{0em}
\setlength{\columnsep}{\TPHorizModule}
\renewcommand\familydefault{\sfdefault}
\renewcommand\sfdefault{phv}
\normalfont
\begin{document}
    \fontsize{9pt}{9pt}\selectfont
    % \setlength{\parskip}{2pt}
    % \setlength{\parindent}{0cm}

    \renewcommand*\arraystretch{1.5}
    \begin{mpxtabular}{>{\raggedright\arraybackslash }p{5.5\TPHorizModule}@{\hspace{\TPHorizModule}}>{\setstretch{1}\raggedright\normalfont\selectfont\arraybackslash}p{5.5\TPHorizModule}}

    \section*{Contractor Agreement} \\

        This Agreement (``Agreement'') is made on \today, (``Effective Date''),
        by and between \textbf{\engineerName{}} (hereafter referred to as the ``Engineer''),
        and \textbf{TechnoPark Corp.} (hereafter referred to as ``TPC''), which
        shall collectively be known as ``Parties''. \\

    \section{Definitions} \\

        ``Activity'' is the smallest piece work performed by Engineer for TPC.
        Activity has a description and a budget in staff-hours.
        Activity can refer to programming, architecture and design, analysis, technical writing,
        system and business analysis, testing, test analysis, planning, risk management, and others,
        according to the Engineer's knowledge, skills, abilities, and certificates. \\

        ``Day'' and ``Daily'' mean ever calendar day, excluding Saturdays, Sundays,
        and official holidays in the country of the Engineer's residence. \\

        ``Confidential Information'' means any and all
        proprietary information disclosed or made available by
        either Party (``Discloser'') hereafter to the other Party (``Holder'') in the course of performing
        activities, whether in written, email, instant message,
        verbal: either by phone or in person, magnetic, photographic,
        optical or other form and whether now existing or hereafter
        created, including, without limitation to, all trade secrets,
        know-how, names and contacts of employees and partners,
        technology, data, computer programs, processes, methods,
        operational procedures, plans, strategies or results, and other
        information of a similar nature that is not generally disclosed
        by the Discloser to the public.
        Confidential Information shall not include any information which
            (a) is proven by written evidence to have been in the Discloser's possession prior to disclosure by the Holder;
            (b) is received from a third party having the right to disclose such information;
            (c) is or hereafter becomes public knowledge through no act or fault of the Discloser; or
            (d) is proven by written evidence to have been independently developed by the Holder without access to the Confidential Information of the Discloser. &
            \M{This definition is very wide, but it covers all possible examples of confidential information, e.g.:
                \begin{itemize}
                \item contact details of TPC's customer,
                \item software code,
                \item ideas and principles of management
                \end{itemize}
            You should be careful with any information you receive during
            your work with TPC. The best approach is to \textbf{not} disclose anything to anyone.} \\

        ``Deliverables'' mean products, services, and results developed
        for and/or delivered to TPC by the Engineer
        during the time of this Agreement. \\

        ``Issue Tracking System (ITS)'' is a computer software package,
        installed and configured by TPC as a web site,
        that manages and maintains lists of Activities. \\

    \section{Recitals} \\

        \N{recitals.1} TPC retains the Engineer to perform
        Activities producing Deliverables in software development projects
        organized and managed by TPC. \\

        \N{recitals.2} TPC agrees to compensate the Engineer using
        the method of calculation explained in this Agreement using
        the price of \textbf{\$\engineerPrice{}} per one staff-hour. \\

        \N{recitals.3} Agreement shall commence on the Effective Date and
        shall remain in force until closure. \\

    \section{Work Order} \\

        \N{order.estimate} TPC shall assign Activities
        to the Engineer in ITS, according to TPC's own plans and judgement.
        The Engineer shall implement Activities
        according to their descriptions. \\

        \N{order.info} TPC shall provide full and complete information
        required by the Engineer for the Activity completeness.
        Parties agree to communicate only through
        ITS. Any other forms of
        communication, like Skype or email, are prohibited.
        Parties shall communicate in
        a professional and respectful manner.
        Parties shall communicate in English. \\

        \N{order.quality} The Engineer shall develop Deliverables according
        to the requirements, guidelines and standards provided by
        TPC before the start of the Activity. &
            \M{We assume that any software products have unlimited amount of defects.
            We don't ask you to produce defect-free products. We ask you
            to deliver result according to requirements. When you estimate
            the activity think about the requirements and ask project manager
            to specify them in proper details.} \\

        \N{order.6} The Engineer shall perform Activities and develop
        Deliverables using his/her own equipment and software,
        including computers, monitors, operating systems, development tools, IDE's, etc. \\

        \N{order.ready} The Engineer shall report in ITS when
        the Deliverables are complete. TPC shall review the Deliverables
        and approve or reject them within 4~(four) days.
        No reply from TPC within specified time interval automatically approves the Deliverables. &
            \M{Once the activity is closed you are not responsible for anything
            that happens with deliverables. If you created a class and it
            was accepted by project manager and activity was closed, all defects
            found later in this class is not your problem.} \\

        \N{order.close} TPC shall close the Activity when all its
        Deliverables are approved. \\

    \section{Activity Termination} \\

        \N{closeout.1} Either Party may terminate an Activity.
        Termination of any Activity does not
        imply closure of the Agreement.\\

        \N{closeout.tpc} TPC may terminate an Activity only if
        its Deliverables are not approved for more
        than 5~(five) days after the recent Activity description
        has been provided to the Engineer. \\

    \section{Payments} \\

        \N{payments.main} TPC shall compensate budgets of all closed Activities
        by ``payments'' sent to the Engineer's accounts (``Payments'')
        TPC shall pay by bank transfer or PayPal. Outgoing bank fees
        and commissions are paid by TPC. \\

        \N{payments.terminated} TPC shall \emph{not} compensate budgets of
        any terminated Activities. \\

        \N{payments.limits} TPC shall send payments on the 1st day of every month,
        if the payment amount is over \$200 (two hundred US dollars) or
        the previous payment was sent earlier than 3~(three) months ago. \\

    \section{Non-Solicitation} \\

        \N{solicitation.1} During the term of this Agreement and for 2~(two)
        years following its termination, the Engineer will not,
        either directly or indirectly, solicit, induce, recruit or
        encourage any employee, customer, or supplier of TPC. \\

    \section{Agreement Closure} \\

        \N{closure.1} Either Party may close the Agreement with or
        without cause by sending a ``notice of closure'' to the
        other Party. \\

    \section{Intellectual Property Rights} \\

        \N{ipr.1} Parties shall deem all Deliverables created by the Engineer
        as ``works made for hire'' as is defined under the
        Copyright Law of the United States of America (edition of June 2003). \\

        \N{ipr.2} The Engineer shall transfer IPR for Deliverables to
        TPC when the Activity is closed. \\

        \N{ipr.3} In the event that Intellectual Property is created, generated, or
        arises under or results from the Engineer's performance under the Agreement
        or from Confidential Information, IPR of such Intellectual Property
        shall vest exclusively with TPC. \\

        \N{ipr.5} The Engineer shall execute all documents, and take any and all
        actions needed, all without further consideration,
        in order to confirm TPC's rights. \\

        \N{ipr.6} The Engineer may mention the projects done for TPC in his personal resume.\\

        \N{ipr.7} TPC shall bear the entire cost pertaining to the assignment. \\

    \section{Confidentiality} \\

        \N{confidentiality.1} Parties shall keep Confidential Information
        in strict confidence and shall not disclose it to any third party or to the public. \\

        \N{confidentiality.10} TPC may use sales materials received from the Engineer
        in its sales and marketing campaigns, including referenced customers names. \\

    \section{Miscellaneous} \\

        \N{misc.2} Where the context so requires or permits, the use of the
        singular form includes the plural, and the use of the plural
        form includes the singular, and the use of any gender
        includes any and all genders. Except as specifically set forth herein,
        all the Article references are to Articles of Agreement and
        all paragraph references (marked as \P) are to paragraphs of the Agreement. \\

        \N{misc.3} Parentheses, capital letters, and quotation marks are
        used merely for the sake of better understanding of context and
        don't impact the meaning of Agreement clauses. \\

    \section{Language and Signatures} \\

        \N{agents.1} The Agreement is written in English
        and both Parties understand its meaning entirely. \\

        \N{agents.2} In witness whereof, Parties hereto have caused the Agreement
        to be executed in the manner appropriate to each as
        of the day and year first written above. \\

        {\raggedright``TPC's Agent'' \\
        {\setstretch{1.2}\fontsize{8pt}{9pt}\selectfont
        \begin{tabular}{|p{5em}|>{\raggedright\arraybackslash}p{18em}|}
        \hline
        Company &       \textbf{TechnoPark Corp.} \\ \hline
        Full name &     Yegor Bugayenko \\ \hline
        Email &         yegor@tpc2.com \\ \hline
        Address &       568 Ninth Street South 202, Naples, Florida, 34102 \\ \hline
        Country &       The United States \\ \hline
        Phone &     +1 (239) 935 5429 \\ \hline
        Signature &     \\[5em] \hline
        \end{tabular}}} \\

        {\raggedright``Engineer'' \\
        {\setstretch{1.2}\fontsize{8pt}{9pt}\selectfont
        \begin{tabular}{|p{5em}|>{\raggedright\arraybackslash}p{18em}|}
        \hline
        Full name &         \textbf{\engineerName} \\ \hline
        Email &         \engineerEmail \\ \hline
        Address &       \engineerAddress \\ \hline
        Country &       \engineerCountry \\ \hline
        Phone &     \engineerPhone \\ \hline
        Signature &     \\[5em] \hline
        \end{tabular}}} \\

    \end{mpxtabular}

\end{document}

